### 2023-10-05 main.tex
fix

We state the following result: the steady state of the Hamiltonian $H^{''}$ is given by 

@@

	|\Psi^{''} \rangle=\sum_{\tau_{1},\ldots,\tau_{L}=1}^{N}\frac{\Gamma\left(2+\sum_{x=1}^{L}\delta_{\tau_{x},N}\right)}{\Gamma\left(L+2\right)}\prod_{x=1}^{L}\left[\lambda_{\tau_{x}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)\right]^{1-\delta_{\tau_{x},N}}|\mathbf{\bm{\tau}}\rangle

@@

We consider the vector with elements given by the operators of the MPA $(X_{1},\ldots,X_{N})$ and we act on it with the similarity transformation $S=S_{2}S_{1}$ obtaining new operators $(\Xt_{1},\ldots,\Xt_{N})$ that will satisfy simpler commutators. 
For the sake of notation, we denote by 

@@

We have

@@

		X_{a}-\beta_{a}\Xt_{N}\\ 
	\end{pmatrix}\qquad \forall a=1,\ldots N-1

@@

Summing over $b\in \{1,\ldots,N\}$ in \eqref{bulk} we have

@@

therefore, we obtain the commutation relations for $\Xt_{a}$ 

@@

where the basis is 

@@

	\widetilde{X}_{a}\widetilde{X}_{N}=\lambda_{a}\widetilde{X}_{N}+\widetilde{X}_{N}\widetilde{X}_{a}
Fix $ a\in \{1,\ldots,N-1\}$ and arbitrary $ \ell,n\in \mathbb{N}$. By applying many times \eqref{UsefulRelation} we have
	\widetilde{X}_{a}^{n}\widetilde{X}_{N}^{\ell}&=\widetilde{X}_{a}^{n-1}\left(\lambda_{a}\widetilde{X}_{1}+\widetilde{X}_{N}\widetilde{X}_{a}\right)\widetilde{X}_{N}^{\ell-1}
	\\&=\lambda_{a}\widetilde{X}_{a}^{n-1}\widetilde{X}_{N}^{b}+\widetilde{X}_{a}^{n-1}\widetilde{X}_{N}\widetilde{X}_{a}\widetilde{X}_{N}^{\ell-1}
	\lambda_{a}\widetilde{X}_{a}^{n-2}\left(\lambda_{a}\widetilde{X}_{N}+\widetilde{X}_{N}\widetilde{X}_{a}\right)\widetilde{X}_{N}^{\ell-1}+\widetilde{X}_{a}^{n-2}\left(\lambda_{a}\widetilde{X}_{N}+\widetilde{X}_{N}\widetilde{X}_{a}\right)\left(\lambda_{a}\widetilde{X}_{N}+\widetilde{X}_{N}\widetilde{X}_{a}\right)\widetilde{X}_{N}^{\ell -1}
	\\&=\ldots\\&=
	\widetilde{X}_{N}^{\ell}\left(\widetilde{X}_{a}+\ell\lambda_{a}\right)^{n}

@@

	\widetilde{X}_{N}^{n_{1}}\ldots\widetilde{X}_{N-1}^{n_{N-1}}\widetilde{X}_{N}^{n_{N}}=\widetilde{X}_{N}^{n_{N}}\prod_{a=1}^{N-1}\left(\widetilde{X}_{a}+n_{N}\lambda_{a}\right)^{n_{a}}

@@

Multiplying by the boundary vectors we have 

@@

	|V \rangle=\langle V^{*}|\widetilde{X}_{N}^{\sum_{i=1}^{L}n_{N}^{l}}\prod_{x=1}^{L}\prod_{a=1}^{N-1}\left(\widetilde{X}_{a}+\lambda_{a}\sum_{j=x}^{L}n_{N}^{j}\right)^{n_{a}^{x}}|V\rangle
Using \eqref{commRIGHT}
	|V \rangle&=\langle V^{*}|\widetilde{X}_{N}^{\sum_{i=1}^{L}n_{N}^{x}}\prod_{x=1}^{L}\prod_{a=1}^{N-1}\left(\lambda_{a}+\lambda_{a}\sum_{j=x}^{L}n_{N}^{j}\right)^{n_{a}^{x}}|V\rangle
	\langle V^{*}|\widetilde{X}_{N}^{\sum_{i=1}^{L}n_{N}^{l}}\prod_{x=1}^{L}\prod_{a=1}^{N-1}\left(\lambda_{a}\right)^{n_{a}^{x}}\left(1+\sum_{j=x}^{L}n_{N}^{j}\right)^{n_{a}^{x}}|V\rangle
	\prod_{x=1}^{L}\prod_{a=1}^{N-1}\left(\lambda_{a}\right)^{n_{a}^{x}}\left(1+\sum_{j=x}^{L}n_{N}^{j}\right)^{n_{a}^{x}}\langle V^{*}|\widetilde{X}_{N}^{\sum_{i=1}^{L}n_{N}^{l}}|V\rangle
To determine the state we now need to compute $\langle V^{*}|\widetilde{X}_{N}^{\sum_{x=1}^{L}n_{N}^{l}}|V\rangle$. Calling $\sum_{x=1}^{L}n_{N}^{x}=n_{N}$ and taking an arbitrary $a\in \{1,\ldots,N-1\}$ we have

@@

@@

		\langle V^{*}|\widetilde{X}_{N}^{n_{N}}|V\rangle=\frac{\Gamma(2+n_{N})}{\Gamma(2+n_{N}-1)}\langle V^{*}|\widetilde{X}_{N}^{n_{N}-1}|V\rangle\\
		\langle V^{*}|\widetilde{X}_{N}^{0}|V\rangle=1
that implies 

@@

	\langle V^{*}|\widetilde{X}_{N}^{n_{N}}|V\rangle&=\frac{\Gamma(2+n_{N})}{\Gamma(2+n_{N}-1)}\langle V^{*}|\widetilde{X}_{N}^{n_{N}-1}|V\rangle=\langle V^{*}|\widetilde{X}_{N}^{n_{N}}|V\rangle=\frac{\Gamma(2+n_{N})}{\Gamma(2+n_{N}-1)}\frac{\Gamma(2+n_{N}-1)}{\Gamma(2+n_{N}-2)}\langle V^{*}|\widetilde{X}_{N}^{n_{N}-2}|V\rangle\\&=

>>>>

We state the following result: the ground state of the Hamiltonian $H^{''}$ is given by 

@@

	|\Psi^{''} \rangle=\sum_{\tau_{1},\ldots,\tau_{L}=1}^{N}\frac{\Gamma\left(2+\sum_{x=1}^{L}\delta_{\tau_{x},N}\right)}{\Gamma\left(2+L\right)}\left(\prod_{x=1}^{L}\left[\lambda_{\tau_{x}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)\right]^{1-\delta_{\tau_{x},N}}\right)|\mathbf{\bm{\tau}}\rangle

@@

We consider the vector with elements given by the operators of the MPA $(X_{1},\ldots,X_{N})$ and we act on it with the similarity transformation $S=S_{2}S_{1}$ obtaining new operators $(\Xt_{1},\ldots,\Xt_{N})$ that will satisfy simpler commutation relations. 
For the sake of notation 

@@

We define the transformed matrix product operators

@@

	\end{pmatrix}%=\begin{pmatrix} 
	%	X_{a}-\beta_{a}\Xt_{N}\\ 
		%	X_{1}+\ldots +X_{N}\\
	%\end{pmatrix}
	\qquad \forall a=1,\ldots N-1

@@

Summing over $b\in \{1,\ldots,N\}$ in commutation relations \eqref{bulk} we have

@@

with $\widetilde{X}_{N}=\widetilde{X}_{1}+\ldots+\widetilde{X}_{1}$, see \eqref{Xtildes2b}. 
Therefore, we obtain the commutation relations for $\Xt_{a}$ 

@@

where the normalization is given by 
		Z_{L}&=\langle V^{*}|(X_{1}+\ldots+X_{N})^{L}|V\rangle=\langle V^{*}|\widetilde{X}_{N}^{L}|V|\rangle\dt
The basis is 

@@

	\widetilde{X}_{a}\widetilde{X}_{N}=\widetilde{X}_{N}\left(\lambda_{a}+\widetilde{X}_{a}\right)
Fix $ a\in \{1,\ldots,N-1\}$ and arbitrary $ \ell,n\in \mathbb{N}$. By applying the above formula \eqref{UsefulRelation} we have
\begin{align}\label{usefulRelaton-many}
	\widetilde{X}_{a}^{n}\widetilde{X}_{N}^{\ell}&=%\widetilde{X}_{a}^{n-1}\left(\lambda_{a}\widetilde{X}_{N}+\widetilde{X}_{N}\widetilde{X}_{a}\right)\widetilde{X}_{N}^{\ell-1}
%	\\&=\lambda_{a}\widetilde{X}_{a}^{n-1}\widetilde{X}_{N}^{\ell}+\widetilde{X}_{a}^{n-1}\widetilde{X}_{N}\widetilde{X}_{a}\widetilde{X}_{N}^{\ell-1}
%	\\&=
%	\lambda_{a}\widetilde{X}_{a}^{n-2}\left(\lambda_{a}\widetilde{X}_{N}+\widetilde{X}_{N}\widetilde{X}_{a}\right)\widetilde{X}_{N}^{\ell-1}+\widetilde{X}_{a}^{n-2}\left(\lambda_{a}\widetilde{X}_{N}+\widetilde{X}_{N}\widetilde{X}_{a}\right)\left(\lambda_{a}\widetilde{X}_{N}+\widetilde{X}_{N}\widetilde{X}_{a}\right)\widetilde{X}_{N}^{\ell -1}
%	\\&=\ldots\\&=
	\widetilde{X}_{1}^{\ell}\left(\widetilde{X}_{a}+\ell\lambda_{a}\right)^{n}

@@

	\widetilde{X}_{1}^{n_{1}}\ldots\widetilde{X}_{N-1}^{n_{N-1}}\widetilde{X}_{N}^{n_{N}}=\widetilde{X}_{N}^{n_{N}}\prod_{a=1}^{N-1}\left(\widetilde{X}_{a}+n_{N}\lambda_{a}\right)^{n_{a}}

@@

Multiplying by the boundary vectors and by using \eqref{commRIGHT} we have 
%	\langle V^{*}|\prod_{x=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{n_{a}^{x}}
%	|V \rangle=\langle %V^{*}|\widetilde{X}_{N}^{\sum_{i=1}^{L}n_{N}^{i}}\prod_{x=1}^{L}\prod_{a=1}^{N-1}\left(\widetilde{X}_{a}+\lambda_{a}\sum_{j=x}^{L}n_{N}^{j}\right)^{n_{a}^{x}}|V\rangle
%Using 

@@

	|V \rangle\nonumber&=\langle V^{*}|\widetilde{X}_{N}^{\sum_{i=1}^{L}n_{N}^{x}}\prod_{x=1}^{L}\prod_{a=1}^{N-1}\left(\lambda_{a}+\lambda_{a}\sum_{j=x}^{L}n_{N}^{j}\right)^{n_{a}^{x}}|V\rangle\nonumber
	\langle V^{*}|\widetilde{X}_{N}^{\sum_{i=1}^{L}n_{N}^{i}}\prod_{x=1}^{L}\prod_{a=1}^{N-1}\left(\lambda_{a}\right)^{n_{a}^{x}}\left(1+\sum_{j=x}^{L}n_{N}^{j}\right)^{n_{a}^{x}}|V\rangle\nonumber
	\prod_{x=1}^{L}\prod_{a=1}^{N-1}\left(\lambda_{a}\right)^{n_{a}^{x}}\left(1+\sum_{j=x}^{L}n_{N}^{j}\right)^{n_{a}^{x}}\langle V^{*}|\widetilde{X}_{N}^{\sum_{i=1}^{L}n_{N}^{i}}|V\rangle
To determine the state we now need to compute $\langle V^{*}|\widetilde{X}_{N}^{\sum_{i=1}^{L}n_{N}^{i}}|V\rangle$. Calling $\sum_{x=1}^{L}n_{N}^{x}=n_{N}$ and using \eqref{commLEFT} for $a\in \{1,\ldots,N-1\}$ we obtain 

@@

where in the second equality we used \eqref{usefulRelaton-many}. 

@@

		\langle V^{*}|\widetilde{X}_{N}^{n_{N}}|V\rangle=\frac{\Gamma(2+n_{N})}{\Gamma(2+n_{N}-1)}\langle V^{*}|\widetilde{X}_{N}^{n_{N}-1}|V\rangle
with $	\langle V^{*}|\widetilde{X}_{N}^{0}|V\rangle=1$. 
Therefore, we obtain 

@@

	\langle V^{*}|\widetilde{X}_{N}^{n_{N}}|V\rangle&=%\frac{\Gamma(2+n_{N})}{\Gamma(2+n_{N}-1)}\langle V^{*}|\widetilde{X}_{N}^{n_{N}-1}|V\rangle=\langle V^{*}|\widetilde{X}_{N}^{n_{N}}|V\rangle=\frac{\Gamma(2+n_{N})}{\Gamma(2+n_{N}-1)}\frac{\Gamma(2+n_{N}-1)}{\Gamma(2+n_{N}-2)}\langle V^{*}|\widetilde{X}_{N}^{n_{N}-2}|V\rangle\\&=
